An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-23 poly-embed-journal/poly-embed-journal.tex
Pass on Section 5 with another attempt at top k

Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option\raft{Let's dump a few citations here, starting with Bartlett~\cite{bartlett2008classification}}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report to the origin. %; let us assume $n = 2^d$ so that we have a bijection
\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use our embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, show inconsistency with respect to 0-1 loss\raft{But it was already known, right?  If so, it's good to use phrases like ``recover the result that''}.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}
The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T,y) &= \sum_{i=1}^{k} |T_{i}| \cdot \Ind{y \not \in T_{i-1}}-1~.~
\end{align*}
\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}

This loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all smaller sets.
\citet{wang2020weston} use our framework to show that $L_{WW}$ embeds $\ell^\OP$, and thus is calibrated with respect to it\raft{Do they construct a link, or start with the existing one?  If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}.
Specifically, they use the embedding
% \citet[Definition 2.3]{wang2020weston}
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\raf{Here would be a good place to define the link $\psi$, even if informally.}

@@

\raf{Take one more pass?  Define the brackets notation.  Feel free to guess at what our results are going to be, and then add margin comments that we should revisit.}
Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.

\begin{align}\label{eq:topk-embedding}
L(u,y) &= \max \left(u_{[1]}, \max_{m \in k+1, \ldots, m} 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]} \right)- u_y
\end{align}

Moreover, \citet{ourtopkpaper} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO... confirm this is true.}
Their proof uses the $\epsilon$-thickened link construction from \S~\ref{sec:calibration} to understand which choices of linked values are feasible and align these choices with the argmax link.

>>>>

Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report to the origin. %; let us assume $n = 2^d$ so that we have a bijection
%\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}
The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T,y) &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}
%\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}

The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, and conclude that $L_{WW}$ is calibrated with respect to $\ell^\OP$\raft{Do they construct a link, or start with the existing one?  If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}\jessiet{They just show embedding and don't provide a link, citing our construction and leaving it to existence}.
Specifically, they use the embedding
% \citet[Definition 2.3]{wang2020weston}
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\raf{Here would be a good place to define the link $\psi$, even if informally.}\jessie{They don't define $\psi$- they just take its existence for granted as a corollary of showing embedding.}

@@

\raf{Take one more pass?  Define the brackets notation.  Feel free to guess at what our results are going to be, and then add margin comments that we should revisit.}
Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.
Moreover, \citeauthor{ourtopkpaper} presents the embedding in Eq.~\eqref{eq:topk-embedding} for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
In Equation~\eqref{eq:topk-embedding}, $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.

\begin{align}\label{eq:topk-embedding}
L(u,y) &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y
\end{align}

Perhaps the most natural link function for a proposed top-$k$ surrogate is the argmax link 
$\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ linking to the $k$ highest elements of $u$.
While the embeddings framework guarantees the existence of a calibrated link, we cannot immediately conclude the pair $(L, \psi^{\tt argmax})$ is calibrated with respect to the top-$k$ loss.
\citeauthor{ourtopkpaper} use the $\epsilon$-thickening link construction as a tool to verify this natural conjecture in the following way:
in constructing an $\epsilon$-thickened link as in \S~\ref{sec:calibration}, the function $\Psi(u)$ yields a set of possible link choices for each $u \in \reals^d$.
Verifying the calibration of a proposed link is accomplished by testing $\psi^{\tt argmax}(u) \in \Psi(u)$ for all $u \in \reals^d$. \btw{COME BACK AND CHECK}

\btw{This entire paragraph is conjecture}
\citeauthor{ourtopkpaper} additionally compare empirical convergence results and error rates of optimizing $L$ and the surrogates of \citet{yang2018consistency,lapin2016loss}.
In low-noise settings, such as cleaned datasets, performance is about equal across surrogates, but in synthetic settings where the distribution of data is approximately uniform, $L$ outperforms inconsistent surrogates, and converges faster than very smooth, highly granular surrogates.
